### 2016-10-04 Chapters/MathematicalResults.tex
DONE

\begin{epigraphs}
\qitem{\textitalian{Non temerai i terrori della notte non temerai il terrore}}{--- \textsc{CCCP}}
\end{epigraphs}

@@

Basic results in the fields of functional analysis and boundary integral
equations that were omitted from Chapter \ref{ch:CSM} are presented here.
No proofs or examples are given, the interested reader is referred to the
monographs by \citeauthor{Ern2004-oo}, \citeauthor{Hsiao2008-xb} and
\citeauthor{Sauter2011-an}\autocite{Ern2004-oo, Hsiao2008-xb, Sauter2011-an}

@@

Carrying out a similarity transformation of
an operator $O$ by means of the $T_1$ cluster operator will preserve the particle
rank of $O$, since $T_1$ is a one-electron operator.\autocite{Koch1994-vr}
Starting from the arbitrary order Lagrangian \eqref{eq:cc-lagrangian},
we want to derive their $T_1$-transformed
expressions.
For the \acrshort{CCS} model, this is straightforward.
The Lagrangian is:
\begin{equation}\label{eq:ccs-lagrangian}
 \mathcal{L}(\tamp{}, \tbar{})_\mathrm{CCS}
 =
  E_0
  + \tbar{\mu_1}\denom{\mu_1}\tamp{\mu_1}
  + \braket{\mathrm{HF} | \check{\Phi} | \mathrm{HF}}
  + \braket{\tbar{1} | \check{\Phi} | \mathrm{HF}}
\end{equation}
the governing equations:
\begin{subequations}\label{eq:ccs-equations}
  \begin{align}
   \denom{\mu_1}\tamp{\mu_1} &+ \braket{\mu_1 | \check{\Phi} | \mathrm{HF}}
             = 0 \label{eq:ccs-amplitudes}\\
    \denom{\mu_1}\tbar{\mu_1} &+
    \braket{\mathrm{HF} | \commutator{\check{\Phi}}{\cluster{\mu_1}} | \mathrm{HF}} +
    \braket{\tbar{1} |
    \commutator{\check{\Phi}}{\cluster{\mu_1}} | \mathrm{HF}}
             = 0 \label{eq:ccs-multipliers}
  \end{align}
\end{subequations}

When including higher order excitations we will seek simplifications in the commutator expansions
by employing the following result:\autocite{Helgaker2000-tz}
\begin{lemma}[Excitation ranks manifold]\label{lemma:exc-rank}
The $k$-fold nested commutator of a \emph{particle rank} $m_O$ operator $O$ with
cluster operators $T_{n_i}$ of rank $n_i$ acting on the reference determinant:
\begin{equation}
  \commutator{\commutator{\commutator{O}{T_{n_1}}}{\ldots}}{T_{n_k}} \ket{\mathrm{HF}}
\end{equation}
generates a linear combination of determinants with excitation ranks $v$ in the
range:
\begin{equation}
  \sum_{i=1}^k n_i - m_O \leq v \leq \sum_{i=1}^k n_i + m_O -k
\end{equation}
\end{lemma}
\begin{corollary}[Excited states overlaps]
The overlap of a determinant $\mu_n$ with excitation rank $n$ onto the linear
combination of determinants generated by the $k$-fold nested commutator of an
operator $O$ with particle rank $m_O$ with cluster operators $T_{n_i}$ of rank $n_i$ is
nonzero if and only if the sum of cluster operator ranks satisfies:
\begin{equation}
  n - m_O + k \leq \sum_{i=1}^k n_i \leq n + m_O
\end{equation}
In compact form:
\begin{equation}
  \braket{\mu_n |
  \commutator{\commutator{\commutator{O}{T_{n_1}}}{\ldots}}{T_{n_k}} | \mathrm{HF}} \neq 0
  \Longleftrightarrow
  n - m_O + k \leq \sum_{i=1}^k n_i \leq n + m_O
\end{equation}
\end{corollary}

The \acrshort{CCSD} Lagrangian is then:
\begin{equation}\label{eq:ccsd-lagrangian}
 \begin{aligned}
 \mathcal{L}(\tamp{}, \tbar{})_\mathrm{CCSD}
&=
 E_0
 + \sum_{u=1}^{2}\tbar{\mu_u}\denom{\mu_u}\tamp{\mu_u}
 + \braket{\mathrm{HF} | \check{\Phi} + \commutator{\check{\Phi}}{T_2} | \mathrm{HF}} \\
 &+ \braket{\tbar{1} | \check{\Phi} + \commutator{\check{\Phi}}{T_2} | \mathrm{HF}} \\
 &+ \braket{\tbar{2} | \check{\Phi} + \commutator{\check{\Phi}}{T_2}
   +\frac{1}{2}\commutator{\commutator{\check{\Phi}}{T_2}}{T_2} | \mathrm{HF}}
  \end{aligned}
\end{equation}
with the governing equations:
\begin{subequations}\label{eq:ccsd-equations}
  \begin{align}
   \denom{\mu_1}\tamp{\mu_1} &+ \braket{\mu_1 | \check{\Phi} + \commutator{\check{\Phi}}{T_2} | \mathrm{HF}}
             = 0 \label{eq:ccsd-singles-amplitudes}\\
   \denom{\mu_2}\tamp{\mu_2} &+
   \braket{\mu_2 | \check{\Phi} + \commutator{\check{\Phi}}{T_2} +\frac{1}{2}\commutator{\commutator{\check{\Phi}}{T_2}}{T_2} | \mathrm{HF}}
             = 0 \label{eq:ccsd-doubles-amplitudes}\\
    \denom{\mu_1}\tbar{\mu_1} &+
    \braket{\mathrm{HF} | \commutator{\check{\Phi}}{\cluster{\mu_1}} | \mathrm{HF}} +
    \braket{\tbar{1} |
      \commutator{\check{\Phi}}{\cluster{\mu_1}}
    + \commutator{\commutator{\check{\Phi}}{\cluster{\mu_1}}}{T_2}
    | \mathrm{HF}} \nonumber \\
   &+ \braket{\tbar{2} |
      \commutator{\check{\Phi}}{\cluster{\mu_1}}
    + \commutator{\commutator{\check{\Phi}}{\cluster{\mu_1}}}{T_2}
    | \mathrm{HF}}
             = 0 \label{eq:ccsd-singles-multipliers} \\
    \denom{\mu_2}\tbar{\mu_2} &+
    \braket{\mathrm{HF} | \commutator{\check{\Phi}}{\cluster{\mu_2}} | \mathrm{HF}} +
    \braket{\tbar{1} |
      \commutator{\check{\Phi}}{\cluster{\mu_2}}
    | \mathrm{HF}} \nonumber \\
   &+ \braket{\tbar{2} |
      \commutator{\check{\Phi}}{\cluster{\mu_2}}
    + \commutator{\commutator{\check{\Phi}}{\cluster{\mu_2}}}{T_2}
    | \mathrm{HF}}
             = 0 \label{eq:ccsd-doubles-multipliers}
  \end{align}
\end{subequations}
Equations \eqref{eq:ccsd-doubles-amplitudes},
\eqref{eq:ccsd-singles-multipliers} and \eqref{eq:ccsd-doubles-multipliers} can
be compared with the corresponding \acrshort{CC2} equations
\eqref{eq:cc2-doubles-amplitudes}, \eqref{eq:cc2-singles-multipliers} and
\eqref{eq:cc2-doubles-multipliers}, respectively, to highlight which terms were neglected in
constructing the iterative method for the approximate inclusion of double excitations.

The \acrshort{CCSDT} Lagrangian is built in the same exact manner:

@@

 + \sum_{u=1}^{3}\tbar{\mu_u}\denom{\mu_u}\tamp{\mu_u}
 + \braket{\mathrm{HF} | \check{\Phi} + \commutator{\check{\Phi}}{T_2} | \mathrm{HF}} \\

@@

 &+ \braket{\tbar{2} | \check{\Phi} + \commutator{\check{\Phi}}{T_2}
   +\frac{1}{2}\commutator{\commutator{\check{\Phi}}{T_2}}{T_2} + \commutator{\check{\Phi}}{T_3} | \mathrm{HF}} \\

@@

   + \frac{1}{2}\commutator{\commutator{\check{\Phi}}{T_2}}{T_2} + \commutator{\check{\Phi}}{T_3}

@@

   \denom{\mu_2}\tamp{\mu_2} &+ \braket{\mu_2 |

@@

   + \frac{1}{2}\commutator{\commutator{\check{\Phi}}{T_2}}{T_2} + \commutator{\check{\Phi}}{T_3}

@@

   \denom{\mu_3}\tamp{\mu_3} &+ \braket{\mu_3 |

@@

   + \frac{1}{2}\commutator{\commutator{\check{\Phi}}{T_2}}{T_2} + \commutator{\check{\Phi}}{T_3}

@@

@@

    +  \commutator{\commutator{\check{\Phi}}{\cluster{\mu_2}}}{T_3}

@@

For the \acrshort{CCS} model, the expectation value of a one-electron operator
is simply:
\begin{equation}\label{eq:ccs-expectation-value}
\begin{aligned}
  O(\tamp{}, \tbar{})_\mathrm{CCS} &=
  \braket{\mathrm{HF} | \check{O} | \mathrm{HF} }
  + \braket{\tbar{1} | \check{O} | \mathrm{HF} } \\
  &=
  \braket{\mathrm{HF} | O + \commutator{O}{T_1} | \mathrm{HF} }
  + \braket{\tbar{1} | O + \commutator{O}{T_1}
  + \frac{1}{2}\commutator{\commutator{O}{T_1}}{T_1} | \mathrm{HF} }
\end{aligned}
\end{equation}
Adding double excitations to the manifold yields:
\begin{equation}\label{eq:ccsd-expectation-value}
  \begin{aligned}
  O(\tamp{}, \tbar{})_\mathrm{CCSD}
  &=
    O(\tamp{}, \tbar{})_\mathrm{CCS}
  + \braket{\tbar{1} | \commutator{\check{O}}{T_2} | \mathrm{HF} }
  + \braket{\tbar{2} | \commutator{\check{O}}{T_2} | \mathrm{HF} } \\
  &=
    O(\tamp{}, \tbar{})_\mathrm{CCS}
  + \braket{\tbar{1} | \commutator{O}{T_2} | \mathrm{HF} }
  + \braket{\tbar{2} | \commutator{O}{T_2}
      + \commutator{\commutator{O}{T_1}}{T_2}
  | \mathrm{HF} },
  \end{aligned}
\end{equation}
where a number of terms was dropped thanks to Lemma \ref{lemma:exc-rank} and its
Corollary.
Eventually, including triples one obtains:
\begin{equation}\label{eq:ccsdt-expectation-value}
\begin{aligned}
  O(\tamp{}, \tbar{})_\mathrm{CCSDT}
  &=
    O(\tamp{}, \tbar{})_\mathrm{CCSD}
  + \braket{\tbar{2} | \commutator{\check{O}}{T_3} | \mathrm{HF} } \\
  &+ \braket{\tbar{3} | \commutator{\check{O}}{T_3}
    + \frac{1}{2}\commutator{\commutator{\check{O}}{T_2}}{T_2}
  | \mathrm{HF} } \\
  &=
    O(\tamp{}, \tbar{})_\mathrm{CCSD}
  + \braket{\tbar{2} | \commutator{O}{T_3} | \mathrm{HF} } \\
  &+ \braket{\tbar{3} | \commutator{O}{T_3}
    + \commutator{\commutator{O}{T_1}}{T_3}
    + \frac{1}{2}\commutator{\commutator{O}{T_2}}{T_2}
  | \mathrm{HF} }
\end{aligned}
\end{equation}
where Lemma \ref{lemma:exc-rank} and its corollary were again extensively employed.

@@

\begin{defin}[Fractional Sobolev spaces]
For $0 < s < 1$ and $1 \leq p < +\infty$, the so-called \emph{Sobolev space with fractional
exponent} is defined as
\begin{equation}
W^{s, p}(\Omega) =
\left\lbrace
u \in L^p(\Omega) |
\frac{u(\vect{r}) - u(\vect{r}^\prime)}{\| \vect{r} - \vect{r}^\prime\|^{s+\frac{d}{p}}}
\in L^p(\Omega \times \Omega)
\right\rbrace.
\end{equation}
Furthermore, when $s> 1$ is not integer, letting $\sigma = s - [s]$, where $[s]$ is the integer
part of $s$, $W^{s,p}(\Omega)$ is defined as
\begin{equation}
W^{s, p}(\Omega) =
\left\lbrace
u \in W^{[s], p}(\Omega) |
\partial^\alpha u \in W^{\sigma, p}(\Omega)\, \forall \alpha,\, |\alpha| = [s]
\right\rbrace.
\end{equation}
When $p=2$, we denote $H^s(\Omega) = W^{s,2}(\Omega)$.
\end{defin}

@@

\begin{lemma}[Integral Representation]
For the transmission problem \ref{eq:transmission-general} there holds:
\begin{enumerate}
\item $\forall \vect{r} \in \Omegai$
\begin{equation}
u = \bi{S}_\mathrm{i}(\partiali u)
- \bi{D}_\mathrm{i}(\ui) + \int_{\Omegai} \Gi f_\mathrm{i}\diff \vect{r}^\prime
\end{equation}
\item $\forall \vect{r} \in \Omegae$
\begin{equation}
u = -\bi{S}_\mathrm{e}(\partiale u)
+ \bi{D}_\mathrm{e}(\ue) + \int_{\Omegae}\Ge f_\mathrm{e}\diff \vect{r}^\prime
\end{equation}
\item $\forall \vect{r} \in \Gamma$
  \begin{equation}\label{eq:stat3}
    \frac{1}{2}\ui = \bi{S}_\mathrm{i}(\partiali u)
    - \bi{D}_\mathrm{i}(\ui) + \int_{\Omegai}\Gi f_\mathrm{i}\diff \vect{r}^\prime
  \end{equation}
\item $\forall \vect{r} \in \Gamma$
  \begin{equation}\label{eq:stat4}
    \frac{1}{2}\ue = -\bi{S}_\mathrm{e}(\partiale u)
    + \bi{D}_\mathrm{e}(\ue) + \int_{\Omegae}\Ge f_\mathrm{e}\diff \vect{r}^\prime
  \end{equation}
\end{enumerate}
\end{lemma}

We introduce the following auxiliary potential:
\begin{subequations}
\begin{empheq}[left={h(\vect{r}) = \empheqlbrace}]{align}
    &\int_{\mathbb{R}^3}\Gi\rhoi(\vect{r}^\prime)\diff \vect{r}^\prime  \quad \vect{r} \in \Omegai \\
    &\int_{\mathbb{R}^3}\Ge\rhoi(\vect{r}^\prime)\diff \vect{r}^\prime  \quad \vect{r} \in \Omegae
\end{empheq}
\end{subequations}
for which we have:
\begin{subequations}
\begin{empheq}[left={\empheqlbrace}]{align}
    \nabla^2 h &= \rhoi \,\, \text{in}\,\, \Omegai \\
    \Le h &= 0 \,\, \text{in}\,\, \Omegae
\end{empheq}
\end{subequations}
We then define the \emph{reaction potential} as:
\begin{equation}
  \xi = u - h
\end{equation}
such that:
\begin{subequations}
  \begin{align}[left={\empheqlbrace}]
  \nabla^2 \xi &= 0 \,\, \text{in}\,\, \Omegai \\
  \Le \xi &= 0 \,\, \text{in}\,\, \Omegae \\
  -[\xi] &= [h] \,\, \text{on}\,\, \Gamma \\
  -[\partial_L \xi] &= [\partial_L h] \,\, \text{on}\,\, \Gamma
\end{align}
\end{subequations}
inside the cavity, the reaction potential can be represented by a
\emph{single layer potential}:
\begin{equation}
  \xi_\mathrm{i} = \bi{S}_\mathrm{i}\sigma
\end{equation}
where the function $\sigma$ is the, yet unknown, \acrlong{ASC}.

>>>>

@@

Basic results in the fields of functional analysis and boundary integral
equations that were omitted from Chapter \ref{ch:CSM} are presented here.
No proofs or examples are given, the interested reader is referred to the
monographs by \citeauthor{Ern2004-oo},\autocite{Ern2004-oo} \citeauthor{Hsiao2008-xb}\autocite{Hsiao2008-xb} and
\citeauthor{Sauter2011-an}\autocite{Sauter2011-an}

@@

Carrying out a similarity transformation of
an operator $O$ by means of the $T_1$ cluster operator will preserve the particle
rank of $O$, since $T_1$ is a one-electron operator.\autocite{Koch1994-vr}
Starting from the arbitrary order Lagrangian \eqref{eq:cc-lagrangian},
we want to derive their $T_1$-transformed
expressions.
\arrowthought{For the \acrshort{CCS} model, this is straightforward.}
The Lagrangian is:
\begin{equation}\label{eq:ccs-lagrangian}
 \mathcal{L}(\tamp{}, \tbar{})_\mathrm{CCS}
 =
  E_0
  + \tbar{\mu_1}\denom{\mu_1}\tamp{\mu_1}
  + \braket{\mathrm{HF} | \check{\Phi} | \mathrm{HF}}
  + \braket{\tbar{1} | \check{\Phi} | \mathrm{HF}}
\end{equation}
the governing equations:
\begin{subequations}\label{eq:ccs-equations}
  \begin{align}
   \denom{\mu_1}\tamp{\mu_1} &+ \braket{\mu_1 | \check{\Phi} | \mathrm{HF}}
             = 0 \label{eq:ccs-amplitudes}\\
    \denom{\mu_1}\tbar{\mu_1} &+
    \braket{\mathrm{HF} | \commutator{\check{\Phi}}{\cluster{\mu_1}} | \mathrm{HF}} +
    \braket{\tbar{1} |
    \commutator{\check{\Phi}}{\cluster{\mu_1}} | \mathrm{HF}}
             = 0 \label{eq:ccs-multipliers}
  \end{align}
\end{subequations}

When including higher order excitations we will seek simplifications in the commutator expansions
by employing the following result:\autocite{Helgaker2000-tz}
\begin{lemma}[Excitation ranks manifold]\label{lemma:exc-rank}
The $k$-fold nested commutator of a \emph{particle rank} $m_O$ operator $O$ with
cluster operators $T_{n_i}$ of rank $n_i$ acting on the reference determinant:
\begin{equation}
  \commutator{\commutator{\commutator{O}{T_{n_1}}}{\ldots}}{T_{n_k}} \ket{\mathrm{HF}}
\end{equation}
generates a linear combination of determinants with excitation ranks $v$ in the
range:
\begin{equation}
  \sum_{i=1}^k n_i - m_O \leq v \leq \sum_{i=1}^k n_i + m_O -k
\end{equation}
\end{lemma}
\begin{corollary}[Excited states overlaps]
The overlap of a determinant $\mu_n$ with excitation rank $n$ onto the linear
combination of determinants generated by the $k$-fold nested commutator of an
operator $O$ with particle rank $m_O$ with cluster operators $T_{n_i}$ of rank $n_i$ is
nonzero if and only if the sum of cluster operator ranks satisfies:
\begin{equation}
  n - m_O + k \leq \sum_{i=1}^k n_i \leq n + m_O
\end{equation}
In compact form:
\begin{equation}
\begin{aligned}
  &\braket{\mu_n |
  \commutator{\commutator{\commutator{O}{T_{n_1}}}{\ldots}}{T_{n_k}} | \mathrm{HF}} \neq 0
  \Longleftrightarrow \\
  &n - m_O + k \leq \sum_{i=1}^k n_i \leq n + m_O
\end{aligned}
\end{equation}
\end{corollary}

\arrowthought{The \acrshort{CCSD} Lagrangian is then:}
\begin{equation}\label{eq:ccsd-lagrangian}
 \begin{aligned}
 \mathcal{L}(\tamp{}, \tbar{})_\mathrm{CCSD}
&=
 E_0
 + \sum_{u=1}^{2}\tbar{\mu_u}\denom{\mu_u}\tamp{\mu_u} \\
 &+ \braket{\mathrm{HF} | \check{\Phi} + \commutator{\check{\Phi}}{T_2} | \mathrm{HF}} \\
 &+ \braket{\tbar{1} | \check{\Phi} + \commutator{\check{\Phi}}{T_2} | \mathrm{HF}} \\
 &+ \braket{\tbar{2} | \check{\Phi} + \commutator{\check{\Phi}}{T_2} | \mathrm{HF}} \\
 &+ \braket{\tbar{2} |
   \frac{1}{2}\commutator{\commutator{\check{\Phi}}{T_2}}{T_2} | \mathrm{HF}}
  \end{aligned}
\end{equation}
with the governing equations:
\begin{subequations}\label{eq:ccsd-equations}
  \begin{align}
   \denom{\mu_1}\tamp{\mu_1} &+ \braket{\mu_1 | \check{\Phi} + \commutator{\check{\Phi}}{T_2} | \mathrm{HF}}
             = 0 \label{eq:ccsd-singles-amplitudes}\\
   \denom{\mu_2}\tamp{\mu_2} &+
   \braket{\mu_2 | \check{\Phi} + \commutator{\check{\Phi}}{T_2} +\frac{1}{2}\commutator{\commutator{\check{\Phi}}{T_2}}{T_2} | \mathrm{HF}}
             = 0 \label{eq:ccsd-doubles-amplitudes}\\
    \denom{\mu_1}\tbar{\mu_1} &+
    \braket{\mathrm{HF} | \commutator{\check{\Phi}}{\cluster{\mu_1}} | \mathrm{HF}} +
    \braket{\tbar{1} |
      \commutator{\check{\Phi}}{\cluster{\mu_1}}
    + \commutator{\commutator{\check{\Phi}}{\cluster{\mu_1}}}{T_2}
    | \mathrm{HF}} \nonumber \\
   &+ \braket{\tbar{2} |
      \commutator{\check{\Phi}}{\cluster{\mu_1}}
    + \commutator{\commutator{\check{\Phi}}{\cluster{\mu_1}}}{T_2}
    | \mathrm{HF}}
             = 0 \label{eq:ccsd-singles-multipliers} \\
    \denom{\mu_2}\tbar{\mu_2} &+
    \braket{\mathrm{HF} | \commutator{\check{\Phi}}{\cluster{\mu_2}} | \mathrm{HF}} +
    \braket{\tbar{1} |
      \commutator{\check{\Phi}}{\cluster{\mu_2}}
    | \mathrm{HF}} \nonumber \\
   &+ \braket{\tbar{2} |
      \commutator{\check{\Phi}}{\cluster{\mu_2}}
    + \commutator{\commutator{\check{\Phi}}{\cluster{\mu_2}}}{T_2}
    | \mathrm{HF}}
             = 0 \label{eq:ccsd-doubles-multipliers}
  \end{align}
\end{subequations}
Equations \eqref{eq:ccsd-doubles-amplitudes},
\eqref{eq:ccsd-singles-multipliers} and \eqref{eq:ccsd-doubles-multipliers} can
be compared with the corresponding \acrshort{CC2} equations
\eqref{eq:cc2-doubles-amplitudes}, \eqref{eq:cc2-singles-multipliers} and
\eqref{eq:cc2-doubles-multipliers}, respectively, to highlight which terms were neglected in
constructing the iterative method for the approximate inclusion of double excitations.

\arrowthought{The \acrshort{CCSDT} Lagrangian is built in the same exact manner:}

@@

 + \sum_{u=1}^{3}\tbar{\mu_u}\denom{\mu_u}\tamp{\mu_u} \\
 &+ \braket{\mathrm{HF} | \check{\Phi} + \commutator{\check{\Phi}}{T_2} | \mathrm{HF}} \\

@@

 &+ \braket{\tbar{2} | \check{\Phi} + \commutator{\check{\Phi}}{T_2} | \mathrm{HF}} \\
   \frac{1}{2}\commutator{\commutator{\check{\Phi}}{T_2}}{T_2} + \commutator{\check{\Phi}}{T_3} | \mathrm{HF}} \\

@@

   + \frac{1}{2}\commutator{\commutator{\check{\Phi}}{T_2}}{T_2}
   | \mathrm{HF}} \\
 &+ \braket{\tbar{3} | \commutator{\check{\Phi}}{T_3} + \commutator{\commutator{\check{\Phi}}{T_2}}{T_3}

@@

   \denom{\mu_2}\tamp{\mu_2}
   &+ \braket{\mu_2 |

@@

   &+ \braket{\mu_2 |
    \frac{1}{2}\commutator{\commutator{\check{\Phi}}{T_2}}{T_2} + \commutator{\check{\Phi}}{T_3}

@@

   \denom{\mu_3}\tamp{\mu_3} &+
   \braket{\mu_3 |

@@

   + \frac{1}{2}\commutator{\commutator{\check{\Phi}}{T_2}}{T_2}
   &+ \braket{\mu_3 |
     \commutator{\check{\Phi}}{T_3}

@@

     \commutator{\commutator{\check{\Phi}}{\cluster{\mu_1}}}{T_3}

@@

      \commutator{\commutator{\check{\Phi}}{\cluster{\mu_2}}}{T_3}

@@

\arrowthought{For the \acrshort{CCS} model, the expectation value of a one-electron operator
is simply:}
\begin{equation}\label{eq:ccs-expectation-value}
\begin{aligned}
  O(\tamp{}, \tbar{})_\mathrm{CCS} &=
  \braket{\mathrm{HF} | \check{O} | \mathrm{HF} }
  + \braket{\tbar{1} | \check{O} | \mathrm{HF} } \\
  &=
  \braket{\mathrm{HF} | O + \commutator{O}{T_1} | \mathrm{HF} } \\
  &+ \braket{\tbar{1} | O + \commutator{O}{T_1}
  + \frac{1}{2}\commutator{\commutator{O}{T_1}}{T_1} | \mathrm{HF} }
\end{aligned}
\end{equation}
Adding double excitations to the manifold yields:
\begin{equation}\label{eq:ccsd-expectation-value}
  \begin{aligned}
  O(\tamp{}, \tbar{})_\mathrm{CCSD}
  &=
    O(\tamp{}, \tbar{})_\mathrm{CCS}
  + \braket{\tbar{1} | \commutator{\check{O}}{T_2} | \mathrm{HF} } \\
  &+ \braket{\tbar{2} | \commutator{\check{O}}{T_2} | \mathrm{HF} } \\
  &=
    O(\tamp{}, \tbar{})_\mathrm{CCS}
  + \braket{\tbar{1} | \commutator{O}{T_2} | \mathrm{HF} } \\
  &+ \braket{\tbar{2} | \commutator{O}{T_2}
      + \commutator{\commutator{O}{T_1}}{T_2}
  | \mathrm{HF} },
  \end{aligned}
\end{equation}
where a number of terms was dropped thanks to Lemma \ref{lemma:exc-rank} and its
Corollary.
Eventually, including triples one obtains:
\begin{equation}\label{eq:ccsdt-expectation-value}
\begin{aligned}
  O(\tamp{}, \tbar{})_\mathrm{CCSDT}
  &=
    O(\tamp{}, \tbar{})_\mathrm{CCSD}
  + \braket{\tbar{2} | \commutator{\check{O}}{T_3} | \mathrm{HF} } \\
  &+ \braket{\tbar{3} | \commutator{\check{O}}{T_3}
    + \frac{1}{2}\commutator{\commutator{\check{O}}{T_2}}{T_2}
  | \mathrm{HF} } \\
  &=
    O(\tamp{}, \tbar{})_\mathrm{CCSD}
  + \braket{\tbar{2} | \commutator{O}{T_3} | \mathrm{HF} } \\
  &+ \braket{\tbar{3} | \commutator{O}{T_3}
    + \commutator{\commutator{O}{T_1}}{T_3}
  | \mathrm{HF} } \\
  &+ \braket{\tbar{3} |
     \frac{1}{2}\commutator{\commutator{O}{T_2}}{T_2}
  | \mathrm{HF} }
\end{aligned}
\end{equation}
where Lemma \ref{lemma:exc-rank} and its corollary were again extensively employed.

@@

\begin{defin}[Fractional Sobolev spaces]
For $0 < s < 1$ and $1 \leq p < +\infty$, the so-called \emph{Sobolev space with fractional
exponent} is defined as
\begin{equation}
W^{s, p}(\Omega) =
\left\lbrace
u \in L^p(\Omega) \Bigg|
\frac{u(\vect{r}) - u(\vect{r}^\prime)}{\| \vect{r} - \vect{r}^\prime\|^{s+\frac{d}{p}}}
\in L^p(\Omega \times \Omega)
\right\rbrace.
\end{equation}
Furthermore, when $s> 1$ is not integer, letting $\sigma = s - [s]$, where $[s]$ is the integer
part of $s$, $W^{s,p}(\Omega)$ is defined as
\begin{equation*}
W^{s, p}(\Omega) =
\left\lbrace
u \in W^{[s], p}(\Omega) |
\partial^\alpha u \in W^{\sigma, p}(\Omega)\, \forall \alpha,\, |\alpha| = [s]
\right\rbrace.
\end{equation*}
When $p=2$, we denote $H^s(\Omega) = W^{s,2}(\Omega)$.
\end{defin}

@@

\begin{lemma}[Integral Representation]
For the transmission problem \ref{eq:transmission-general} there holds:
\begin{enumerate}
\item $\forall \vect{r} \in \Omegai$
\begin{equation}
u = \bi{S}_\mathrm{i}(\partiali u)
- \bi{D}_\mathrm{i}(\ui) + \int_{\Omegai}\diff \vect{r}^\prime \Gi f_\mathrm{i}
\end{equation}
\item $\forall \vect{r} \in \Omegae$
\begin{equation}
u = -\bi{S}_\mathrm{e}(\partiale u)
+ \bi{D}_\mathrm{e}(\ue) + \int_{\Omegae}\diff \vect{r}^\prime\Ge f_\mathrm{e}
\end{equation}
\item $\forall \vect{r} \in \Gamma$
  \begin{equation}\label{eq:stat3}
    \frac{1}{2}\ui = \bi{S}_\mathrm{i}(\partiali u)
    - \bi{D}_\mathrm{i}(\ui) + \int_{\Omegai}\diff \vect{r}^\prime\Gi f_\mathrm{i}
  \end{equation}
\item $\forall \vect{r} \in \Gamma$
  \begin{equation}\label{eq:stat4}
    \frac{1}{2}\ue = -\bi{S}_\mathrm{e}(\partiale u)
    + \bi{D}_\mathrm{e}(\ue) + \int_{\Omegae}\diff \vect{r}^\prime\Ge f_\mathrm{e}
  \end{equation}
\end{enumerate}
\end{lemma}

We introduce the following auxiliary potential:
\begin{subequations}
\begin{empheq}[left={h(\vect{r}) = \empheqlbrace}]{align}
    &\int_{\mathbb{R}^3}\diff \vect{r}^\prime\Gi\rhoi(\vect{r}^\prime)  \quad \vect{r} \in \Omegai \\
    &\int_{\mathbb{R}^3}\diff \vect{r}^\prime\Ge\rhoi(\vect{r}^\prime)  \quad \vect{r} \in \Omegae
\end{empheq}
\end{subequations}
for which we have:
\begin{subequations}
\begin{empheq}[left={\empheqlbrace}]{align}
    \nabla^2 h &= \rhoi \,\, \text{in}\,\, \Omegai \\
    \Le h &= 0 \,\, \text{in}\,\, \Omegae
\end{empheq}
\end{subequations}
We then define the \emph{reaction potential} as:
\begin{equation}
  \xi = u - h
\end{equation}
such that:
\begin{subequations}
  \begin{align}[left={\empheqlbrace}]
  \nabla^2 \xi &= 0 \,\, \text{in}\,\, \Omegai \\
  \Le \xi &= 0 \,\, \text{in}\,\, \Omegae \\
  -[\xi] &= [h] \,\, \text{on}\,\, \Gamma \\
  -[\partial_L \xi] &= [\partial_L h] \,\, \text{on}\,\, \Gamma
\end{align}
\end{subequations}
inside the cavity, the reaction potential can be represented by a
\emph{single layer potential}:
\begin{equation}
  \xi_\mathrm{i} = \bi{S}_\mathrm{i}\sigma
\end{equation}
where the function $\sigma$ is the, yet unknown, \acrlong{ASC}.

To derive an equation for $\sigma$, we set up a system of equations containing
the jump conditions and the integral representations of the reaction and auxiliary potentials:
\begin{subequations}
\begin{empheq}[left={\empheqlbrace}]{align}
    &\bi{S}_\mathrm{i}(\partiali \xi) - \bi{D}_\mathrm{i}(\xi_\mathrm{i})
    = \frac{1}{2}\xi_\mathrm{i} \label{eq:first} \\
    &\bi{S}_\mathrm{e}(\partiale \xi) - \bi{D}_\mathrm{e}(\xi_\mathrm{e})
    = -\frac{1}{2}\xi_\mathrm{e} \label{eq:second} \\
  &\bi{S}_\mathrm{e}(\partiale h) - \bi{D}_\mathrm{e}(h_\mathrm{e})
  = -\frac{1}{2}h_\mathrm{e} \label{eq:third} \\
  &\xi_\mathrm{i} - \xi_\mathrm{e} = h_\mathrm{e} - h_\mathrm{i}
  \label{eq:fourth} \\
  &\partiali \xi - \partiale \xi = \partiale h - \partiali h
  \label{eq:fifth}
\end{empheq}
\end{subequations}
The final ingredient is the \gls{DtN} map, which can be derived by employing Eq. \eqref{eq:stat3}
to the Newton potential:
\begin{equation}
  \phi(\vect{r}) = (\bi{N}\rhoi)(\vect{r}) = \int_{\mathbb{R}^3}\diff \vect{r}^\prime\Gi\rhoi(\vect{r}^\prime)
   = \left.h(\vect{r})\right|_{\Omegai}
\end{equation}
which is equal, in $\Omegai$, to the auxiliary potential $h(\vect{r})$.
The \acrshort{DtN} map is thus given as:
\begin{equation}\label{eq:regular-DtN}
   \left(\frac{1}{2} - \bi{D}_\mathrm{i}\right)\phi_\mathrm{i}
      +\bi{S}_\mathrm{i}(\partiali \phi) = 0
\end{equation}
With this last ingredient at hand, algebraic manipulations lead to the \acrshort{IEF}
equation:
\begin{equation}
  \begin{aligned}
  \big[ \bi{S}_\mathrm{e}\big(2\pi + \bi{D}^\dagger_\mathrm{i}\big)
  &+
  \big(2\pi - \bi{D}_\mathrm{e}\big)\bi{S}_\mathrm{i}
  \big]\sigma = \\
  &-\big[\big(2\pi-\bi{D}_\mathrm{e}\big)
  -\bi{S}_\mathrm{e}\bi{S}_\mathrm{i}^{-1}
  \big(2\pi-\bi{D}_\mathrm{i}\big)
  \big]\esp,
  \end{aligned}
  \tag{\ref{eq:full-IEF} from Chapter \ref{ch:CSM}}
\end{equation}
